---
title: "Alcohol vs Seat choice"
author: "Issa Darrouj"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people sitting in the middle is the highest (89) between the number of people sitting in the front (40) and the back (36). However, the standard deviation of the people sitting in the back is the highest (12.580471) compared to the people sitting in the front (3.806013) and the middle (6.225381).  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the P-value which was about 0.000116, I noticed that it is really small, and telling me that there is a big statistical difference between the values. 

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence level. I saw the confidence intervals of the Front-Back, Middle-Back, and Middle-Front seats, with 0 indicating if the lines are significantly different or not. When I observed the results, I noticed that the Front-Back and the Middle-Back are indeed significantly different, since 0 doesn't go through their confidence intervals. However, for the Middle-Front seats, 0 does go through the confidence interval, and so indicating that there is no significant difference between them. 

## Conclusions

What I learned in today's lesson is looking at numerical categorical data, but the difference this time is that there are more different categories, and so I used my helper file and went down to One Way Anova to help me solve this assignment. It is more complicated than the last numerical categorical data I did, but I was able to get the hang of it. One Way Anova provided me with numerical and inferential results I needed. For instance, the numerical results showed me the number of people sitting in the front, middle, and back lines, and I was able to see the number of people in each row, with the middle row having the highest number of people with 89 seats. I was also able to get the standard deviation values of each line, and got that the back line had the highest standard deviation with 12.580471. The inferential results provided me with the P-value and it was really small (0.000116), which told me that the results are significantly different, and so I went ahead and plotted a 95% confidence level chart to be able to dive more in the results. I noticed that the Front-Back and the Middle-Back are indeed significantly different, since 0 doesn't go through their confidence intervals. However, for the Middle-Front seats, 0 does go through the confidence interval, and so indicating that there is no significant difference between them.  
